Practicing with Survival Analysis

### 2017-07-12 practice_survivalanalysis.Rmd
changed formatting of axes in hazard and survival plots

#cb <- confBands(surv_object, confLevel=0.95, type="hall") #for confidence bands
plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability")
#lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
#lines(cb$time, cb$upper, lty=3, type="s")
```

### instantaneous hazard using epiR package
```{r}
library(epiR)
h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s")
plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s")
#there is a spike in instantaneous hazard before 200,000 seconds (55.5 hours or 2.31 days)
```

@@

#plotting both KM and Nelson Aalen on same graph
plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s")
points(c(fit$time, 6500000), H.tilde, lty=2, type="s")
legend("bottomright", legend=c("H.hat","H.tilde"), lty=1:2)
#KM and Nelson Aalen estimators look the same- because large data set? 
#Rate of increase in cumulative hazard spikes up drastically (immediately after question is posted)- indicating that hazard is increasing on that interval. Rate of increase in cumulative hazard after a certain point, levels out pretty quickly- indicating that hazard is decreasing
```

### mean, medians, percentiles 
```{r}
#at 30,158 seconds (502.6 min, 8.38 hours), 50% of the questions have been answered
#mean survival time = 2,748,083 (45801.38 min, 763.3563hrs, 31.8 days)
#upper limit = largest observation in time to event var
print(KM.obj, print.rmean=TRUE)

@@

* interpreting quantiles: 
* at time = 138 seconds (2.3 min), 1% of the questions have been answered
*           802 seconds (13.4 min), 10% of the questions have been answered
*           2,883 seconds (48.1 min), 25% of the questions have been answered

### exploring time_until_answered
* largest time_until_answered = 89.97 days (obs = 7807), and is censored
* shortest time_until_answered = 23 seconds (obs = 7485) 
```{r}
sum(out1$answered)/length(out1$answered)
#64.4% of observations are complete
#35.6% of observations are censored

library(ggplot2)
ggplot(out1, aes(x = time_until_answer)) + 
  geom_histogram() + 
  scale_x_continuous(limits = c(20, 30000))
```

>>>>

#defining tick marks for x-axis
min <- min(out_english$time_until_answer)
max <- max(out_english$time_until_answer)

#cb <- confBands(surv_object, confLevel=0.95, type="hall") #for confidence bands
plot(KM.obj, main = "KM Curve", xlab = "Seconds", ylab = "Surival Probability", xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE) #adding more detailed x axis
#lines(cb$time, cb$lower, lty=3, type="s") #for confidence bands
#lines(cb$time, cb$upper, lty=3, type="s")
```

### instantaneous hazard using epiR package
```{r}
library(epiR)
h.hat <- epi.insthaz(KM.obj, conf.level = 0.95)
plot(h.hat$time, h.hat$est, main = "h(t) plot", xlab = "Time", ylab = "Hazard Rate", type = "s", xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)

plot(h.hat$time, h.hat$est, main = "h(t) plot (zoomed in)", xlab = "Time", ylab = "Hazard Rate", xlim = c(20,1000000), type = "s", xaxt = "n")
axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)

#there is a spike in instantaneous hazard before 200,000 seconds (55.5 hours or 2.31 days)
```

@@

#plotting both KM and Nelson Aalen on same graph
plot(c(fit$time, 6500000), H.hat, xlab="Time", ylab="Cumulative Hazard", ylim = range(c(H.hat, H.tilde)), type = "s", xaxt = "n")
points(c(fit$time, 6500000), H.tilde, lty=2, type="s", xaxt = "n")
legend("bottomright", legend=c("H.hat","H.tilde"), lty=1:2)
axis(side = 1, at = seq(min, max, by = (max-min)/10), tick = TRUE)
#KM and Nelson Aalen estimators look the same- because large data set? 
#Rate of increase in cumulative hazard spikes up drastically (immediately after question is posted)- indicating that hazard is increasing on that interval. Rate of increase in cumulative hazard after a certain point, levels out pretty quickly- indicating that hazard is decreasing
```

### mean, medians, percentiles 
```{r}
#to get mean and median
print(KM.obj, print.rmean=TRUE)

@@
